---
title: "Weight of Fish"
author: "Mariahlynn"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}

if(!require("Bolstad")) {install.packages("Bolstad");require("Bolstad")}
```



## Perch

### Best Models

```{r}
perchModel=lm(Weight~ .,data=Perch)
summary.lm(perchModel)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model
```{r}
Perch2=lm(Weight~Height+Width,data=Perch)
summary.lm(Perch2)
```
The best two regressor model predict weight using Height and Width.

## Pike
```{r}
pikeModel=lm(Weight~.,data=Pike)
summary.lm(pikeModel)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


### Best Models

```{r}
Pike2=lm(Weight~Length1+Length3,data=Pike)
summary.lm(Pike2)
```

### Best Two regressor model

The best two regressor model to predict weight is length1 and length3. 

## Roach

```{r}
roachModel=lm(Weight~.,data=Roach)
summary.lm(pikeModel)
```



### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


### Best Two regressor model

```{r}
Roach2Model=lm(Weight~Length3+Width,data=Roach)
summary.lm(Roach2Model)
```
The best regressor models for predicting weight for roach are width and length3. 

## Final Summary Statements

The best regressor modles for perch were height and width.

The best regressor for pike were length 1 and length 3.

The best regressor modles for roach were length 3 and width. 



